Local-global principle for $\K_2$ of Chevalley groups

### 2015-09-28 paper.tex
Fixed bug in the notation

\begin{dfn}
 The relative Steinberg group $\St^*(n,R, I)$ is the group defined by the following two
 families generators and four families of relations.
 \begin{itemize}
  \item Generators:
  \begin{enumerate}
  \item $X^1(u, v)$, where $u \in \E(n,R) \cdot e_1$, $v\ \in I^n$ such that $v^t \cdot u = 0$;
  \item $X^2(u, v)$, where $u \in I^n$, $v \in \E(n,R) \cdot e_1$ such that $v^t \cdot u = 0$.
 \end{enumerate}
  Notice that the canonical image in $\E(n, R)$ of both $X^1(u, v)$ and $X^2(u, v)$ equals $T(u, v) = e_n + u \cdot v^T$.
  \item Relations:
  \begin{enumerate}
  \item $X^1(u, v) \cdot X^1(u, w) = X^1(u, v+w)$, $u \in \E(n,R) \cdot e_1$, $v, w \in I^n$;
  \item $X^2(u, v) \cdot X^2(w, v) = X^2(u+w, v)$, $u, w \in I^n$, $v \in \E(n,R) \cdot e_1$;
  \item ${}^{X^\sigma(u^2, v^2)} \! X^\tau(u^1, v^1) = X^\tau(T(u^2, v^2) \cdot u^1, T(v^2, u^2)^{-1} \cdot v^1)$, $\sigma, \tau = 1..2$;
  \item $X^1(u, vb) = X^2(ub, v)$ for $(u,v) \in E(n,R) \cdot (e_1, e_2)$, $b\in I$.
 \end{enumerate}
 \end{itemize}
\end{dfn}
It is easy to check the correctness of the above definition.

@@

Assume that $n \geq 4$. For the rest of this section $a$ denotes a nonnilpotent element of $R$.
\begin{lemma}
 Let $u, v \in R^n$ be columns such that $v^t \cdot u = 0$ and there exists $w = w(u) \in R^n$ satisfying $w^t \cdot u = a^N$ for some natural number $N$.
 In this context one can define certain elements $Z^{1}(u,v), Z^{2}(v, u)$ of $\St(n, R)$. These elements satisfy the following relations:
 \begin{itemize}
  \item $Z^{1}(u, v_1 + v_2) = Z^{1}(u, v_1) \cdot Z^{1}(u, v_2)$;
  \item $Z^{2}(v_1 + v_2, u) = Z^{2}(v_1, u) \cdot Z^{2}(v_2, u)$;
  \item ${}^{g}\! Z^{\tau}(u, v) = Z^{\tau}(g \cdot u, g^* \cdot v)$, $\tau = 1..2$, $g \in \St(n, R)$ where $g^* = {g^t}^{-1}$ is the contragradient matrix.
 \end{itemize}
\end{lemma}
\begin{proof} Both the construction of $Z^i$ and the relations for $Z^i$ are, in essence, just~\cite[Lemma~1.3]{T} applied twice. \end{proof}

>>>>

\begin{dfn}
 The relative Steinberg group $\St^*(n,R, I)$ is the group defined by the following two
 families generators and four families of relations.
 \begin{itemize}
  \item Generators:
  \begin{enumerate}
  \item $X^1(u, v)$, where $u \in \E(n,R) \cdot e_1$, $v\ \in I^n$ such that $v^t \cdot u = 0$;
  \item $X^2(u, v)$, where $u \in I^n$, $v \in \E(n,R) \cdot e_1$ such that $v^t \cdot u = 0$.
 \end{enumerate}
  Notice that the canonical image in $\E(n, R)$ of both $X^1(u, v)$ and $X^2(u, v)$ equals $T(u, v) = e_n + u \cdot v^T$.
  \item Relations:
  \begin{enumerate}
  \item $X^1(u, v) \cdot X^1(u, w) = X^1(u, v+w)$, $u \in \E(n,R) \cdot e_1$, $v, w \in I^n$;
  \item $X^2(u, v) \cdot X^2(w, v) = X^2(u+w, v)$, $u, w \in I^n$, $v \in \E(n,R) \cdot e_1$;
  \item ${}^{X^\sigma(u^2, v^2)} \! X^\tau(u^1, v^1) = X^\tau(T(u^2, v^2) \cdot u^1, T(v^2, u^2)^{-1} \cdot v^1)$, $\sigma, \tau = 1..2$;
  \item $X^1(g \cdot e_1, g^* \cdot be_2) = X^2(g \cdot be_1, g^* \cdot e_2)$ where $g^* = {g^t}^{-1}$ is the contragradient matrix and $b\in I$.
 \end{enumerate}
 \end{itemize}
\end{dfn}
It is easy to check the correctness of the above definition.

@@

Assume that $n \geq 4$. For the rest of this section $a$ denotes a nonnilpotent element of $R$.
\begin{lemma}
 Let $u, v \in R^n$ be columns such that $v^t \cdot u = 0$ and there exists $w = w(u) \in R^n$ satisfying $w^t \cdot u = a^N$ for some natural number $N$.
 In this context one can define certain elements $Z^{1}(u,v), Z^{2}(v, u)$ of $\St(n, R)$. These elements satisfy the following relations:
 \begin{itemize}
  \item $Z^{1}(u, v_1 + v_2) = Z^{1}(u, v_1) \cdot Z^{1}(u, v_2)$;
  \item $Z^{2}(v_1 + v_2, u) = Z^{2}(v_1, u) \cdot Z^{2}(v_2, u)$;
  \item ${}^{g}\! Z^{\tau}(u, v) = Z^{\tau}(g \cdot u, g^* \cdot v)$, $\tau = 1..2$, $g \in \St(n, R)$.
 \end{itemize}
\end{lemma}
\begin{proof} Both the construction of $Z^i$ and the relations for $Z^i$ are, in essence, just~\cite[Lemma~1.3]{T} applied twice. \end{proof}

\begin{lemma}
 For $u_1, u_2 \in R^n$ be columns such that $\overline{u_1} = g \cdot e_1$, $\overline{u_2} = g^* \cdot e_2$ for some $g \in \E(n, R_a)$.
 Then for any $b\in I$ and $g',g'' \in M(n, R)$ such that $\overline{g'} = g$, $\overline{g''} = g^*$ one has 
 $$Z^1(g' \cdot e_1, g'' \cdot be_2) = Z^2(g' \cdot be_1, g'' \cdot e_2).$$
\end{lemma}
